### 2016-07-13 Docs/architecture/architecture.tex
update EOS stuff to refer to Microphysics

Presently there are 3 equations of state that work with \maestro:
\begin{itemize}
\item {\tt helmeos/} represents a general stellar equation 
      of state, consisting of nuclei (as an ideal gas), radiation,
      and electrons (with arbitrary degeneracy and degree of relativity).
      This equation of state is that described in \cite{timmes_eos}.

>>>>

Presently there is a single EOS that comes with \maestro, {tt gamma\_law\_general},
but many more are available through the external \microphysics\ repo\footnote{\microphysics\ is
available at \url{https://github.com/BoxLib-Codes/Microphysics}.  \maestro\ will
find it via the {\tt MICROPHYSICS\_HOME} environment variable}.  The \microphysics\
EOSs share the same interface and can be compiled into \maestro\ directly.  
Here are the more popular EOSs:
\begin{itemize}
\item {\tt helmeos} represents a general stellar equation 
      of state, consisting of nuclei (as an ideal gas), radiation,
      and electrons (with arbitrary degeneracy and degree of relativity).
      This equation of state is that described in \cite{timmes_eos}.
